% !TeX program = LuaLaTeX
\documentclass{template}

\setname{Peter Mezei}{}
\setaddress{Nyíregyháza/Hungary}
\setmobile{+36 30 437 54 90}
\setmail{mezeipetister@gmail.com}
\setposition{Software Engineer} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/peter-mezei-87913760/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/mezeipetister} %you can play with color of the template (red is also nice..)
\setthemecolor{red} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
\\
\vspace{1pt}
\centering
Curriculum Vitae
\\
\vspace{20pt}

\raggedright
% Summary
\addblocktext{Summary}{%
I was born in 15th October 1988. Married, father of two children. Enthusiastic linux user \& rust developer. Fall in love with Open Source \& Free Software. Hard working, creative, love to learn. Robust problem solving. Great communicator, love to lead dev teams \& new projects.
Interested in new technologies and mainly bring modern technologies into farming.
}
%
%Education
\section{Education}
\datedexperience{University of Debrecen, Hungary}{2008-2010}
\explanation{Business Administration and Management, (Marketing), Bsc}
\datedexperience{Groupe ESC Troyes, France}{2010}
\explanation{International Marketing, Erasmus}
\datedexperience{University of Debrecen, Hungary}{2010-2012}
\explanation{Management and Leadership, Controlling, Msc}
\datedexperience{University of Debrecen, Hungary}{2012-2014}
\explanation{Doctoral School of Economics, Marketing}
\explanationdetail{\coloredbullet\ %
  Started my PhD in viral marketing. Paused due to my CEO duties.
}
\datedexperience{CEU, Hungary, UK}{2016}
\explanation{Global Business Felloship}
\explanationdetail{\coloredbullet\ %
  Special CEU startup program for Startup CEOs
}
%
% Experience
\section{Experience}
%
\datedexperience{Webshop-Experts Ltd.}{2010-2012}
\explanation{E-commerce project manager.}
\explanationdetail{\coloredbullet\
Helped dev team about customer feedbacks;
managed new products development; communication between devs and customers.}
%
\datedexperience{Slamby Semantics Ltd.}{2012-2018}
\explanation{Founder, Head of Product Development \& CEO}
\explanationdetail{\coloredbullet\
Opensource Machine Learning AI Startup Company, specialized in automated text categorization for classified ad sites. Main customer was Schibsted. I was responsible for company vision, sales, team motivation, product development. My daily core team job was being a scrum master, \& helping the team to identify and integrate new technologies. Github repo: https://github.com/slamby}
%
\datedexperience{Gardenova Ltd.}{2018-present}
\explanation{Head of New Product Development}
\explanationdetail{\coloredbullet\
Agricultural company, core activity is apple \& sour cherry farming. Helped to find new business opportunities, found a new nice (fresh apple jouce production). Build up sub-project and a new small apple juice manufacturing unit. Designed the whole IT backend to register and maintain LOTs. Built an internal ERP software using Rust and microservices. Desinged and built an online store using TS and NuxtJs.}
%
\datedexperience{Gardenzilla Ltd.}{2021-present}
\explanation{Founder, CTO}
\explanationdetail{\coloredbullet\
Offline and online garden store. Designed and built up a robust backend ERP using Rust and microservice architecture. Built a POS using Rust, TS \& Angular. Using Rust we had a 99.9\% uptime, had no software related issues \& achieved a very rapid product development without extra testing or maintenance.}
%
% Skills
\section{Skills}
%
\newcommand{\skilla}{\createskill{Programming Languages}{Rust \cpshalf Javascript \cpshalf Typescript \cpshalf HTML \cpshalf CSS \cpshalf Bash \cpshalf Python \cpshalf Latex \cpshalf Makefile}}
\newcommand{\skillb}{\createskill{}{Dart \cpshalf RLang \cpshalf C}}
%
\newcommand{\skillc}{\createskill{Software}{Linux \cpshalf Windows (95-11) \cpshalf OSX \cpshalf Microsoft Office \cpshalf Libre Office \cpshalf Matlab \cpshalf R}}
\newcommand{\skilld}{\createskill{}{Photoshop \cpshalf Inkspace \cpshalf Gimp}}
\newcommand{\skille}{\createskill{Software Development}{Programming Paradigms \cpshalf GIT \cpshalf CLI \cpshalf Agile Methodology \cpshalf Scrum \cpshalf Full Stack}}
%
\newcommand{\skillf}{\createskill{Frameworks \ \& \ Libraries}{Warp \cpshalf Rocket \cpshalf Proto3 \cpshalf Angular \cpshalf Nuxt (Vue)}}
%
\createskills{\skilla, \skillb, \skillc, \skilld, \skille, \skillf}
%
% Experience
\section{Extra}
\newcommand{\extraone}{%
  Favourite linux distro: Fedora + Gnome
}
%
\newcommand{\extratwo}{%
  Would love to, but had no time for it: learn guitar, finish my PhD
}
%
\newcommand{\extrathree}{%
  My favourites: Star Trek (TV Series), Big Bang Theoriy (TV Series), Orwell 1984 (Book), John Lennon - Stand by me (Music)
}
%
\newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
%
\createbullets{\listofextras}
%
%Footnote
\createfootnote
\end{document}